(An introduction to )MultiSymplectic Geometry and Classical Field systems

### 2019-03-29 ms-mechanics.tex
Tiny update in ms-mechanics notes

\usepackage{amsmath}
\usepackage[multisym, geomec, basic, diffgeo]{./Math-Symbols-List/toninus-math-symbols}
\usepackage[subpreambles=true]{standalone}
\usepackage{commath}

@@

\usepackage{graphicx}
\usepackage{hyperref}

%\usepackage{Latex-Theorem/theoremtemplate}

%	\renewcommand{\AffDualJet}{ J^{1 \TwistedAffine}E }
%	\renewcommand{\LinDualJet}{ \overrightarrow{J^{1 \TwistedLinear}E} }

@@

$$
\ast 
\star 
\oast 
\ostar
\smoast
\smostar
J^\smostar
J^\smoast
J^\ostar
$$

@@

Classicamente: DOF come numero di misure necessarie per fissare univocamente una configurazione.
\begin{table}[]
\begin{tabular}{lll}
	System & Configuration space (locally) & protoype 
 	\\
	Ordinary system & $\mathbb{R}^n$ with $n\in \mathbb{N} = Hom_{set}(\{1,\ldots n\}, \mathbb{R})$ & A point on a $n$-dimensional mfd.
	\\
	1 dimensional field & $\mathbb{R}^\mathbb{R} = C^\infty(\mathbb{R},\mathbb{R})$ & collection of points on a line each one parametrized by ...
	\\
	n dimensional field & $(\mathbb{R}^m)^{\mathbb{R}^n} = C^\infty (\mathbb{R}^n, \mathbb{R}^m)$ & ...
\end{tabular}
\end{table}

>>>>

\usepackage{amsmath}
\usepackage{amsfonts}
%\usepackage[multisym, geomec, basic, diffgeo]{./Math-Symbols-List/toninus-math-symbols}
\usepackage[subpreambles=true]{standalone}
\usepackage{commath}

@@

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{tabularx}

@@

$$
\ast 
\star 
\oast 
\ostar
\smoast
\smostar
J^\smostar
J^\smoast
%J^\ostar
$$

@@

Classicamente: DOF come numero di misure necessarie per fissare univocamente una configurazione.

\begin{tabularx}{\textwidth}{c X c c}
	System & Prototype & DoF & Configuration space (locally)\\
	Ordinary classical mech system & point-particle on a  $q$-dim manifold &
	$q$ finite (discrete) & $\mathbb{R}^n = Hom_{set}(\{1,\ldots n\}, \mathbb{R})$ \\
	1-dim. field & collection of points on a line each one parametrized by a point on the manifold $Q$ & $q$ for each point on the continuous line (infinite and continuous) &
	...
%	\\
%	n dimensional field & $(\mathbb{R}^m)^{\mathbb{R}^n} = C^\infty (\mathbb{R}^n, \mathbb{R}^m)$ & ...
\end{tabularx}
